Uneven Investments in Toronto's Wards

### 2024-09-27 paper/paper.qmd
finished references

These datasets were merged in order to link capital funding allocations with socioeconomic indicators at the ward level. The analysis for this paper was conducted using @citeR, with several packages from the @tidyverse suite such as @readr which was used to read in files, @stringr which was used for data cleaning and @dplyr which was used for data manipulation. Visualizations were created using @ggplot2, and tables were rendered using @knitr.

>>>>

These datasets were merged in order to link capital funding allocations with socioeconomic indicators at the ward level. The analysis for this paper was conducted using @citeR, with several packages from the @tidyverse suite such as @readr (for reading in files), @stringr (for data cleaning) and @dplyr (for data manipulation). Visualizations were created using @ggplot2, and tables were rendered using @knitr.
